---
title: "Descriptives EFRE-study"
author: "Jule Schilling"
date: "2026-07-22"
format: 
  html:
    embed-resources: true
    toc: true
    toc-depth: 4
    toc-expand: true
    toc-title: "Table of Contents"
execute:
  echo: false      # Hides R code globally across all chunks
  warning: false   # Mutes warnings globally
  message: false   # Mutes package loading messages globally
---

```{r setup, include=FALSE}
setwd("~/Desktop/Uni Würzburg/Forschung/EFRE_Studie/Data/Data_EFRE")
load("EFRE_data.Rdata")

library(dplyr)
library(psych)
```

In this document: Sample characteristics, means, standard deviations and Cronbach's alphas for all questionnaires.

## Sample

Sample size N = 353

Excluded people: n = 21 took less than 15 minutes for the whole study (pre-registered)

n = 2 did not take the study seriously (pre-registered)

```{r}
#| label: demographics sample
#| echo: false
# sex and age of sample
table(data_basic$DM02)
mean(data_basic$DM01_01)
```

### Experience with and Knowledge of Automation

scale: 1 (very little) - 7 (very much)

```{r}
#| label: automation literacy sample
#| echo: false
mean(data_basic$CN01)
mean(data_basic$CN02)
```

## Variables

Depression (Allgemeine Depressionsskala - Kurzform), *Scale: 1-4*

Trust in Automation (Avatar Trust Scale modified; also includes items for trust in humans), *Scale: 1 - 5* (*Anmerkung an mich: ggf. Avatar Scales zusammenfassen und Human Scale separat lassen*)

Big Five (Big Five Inventory Short version), *Scale: 1 - 5*

Coping Style (Coping Inventar zum Umgang mit Stress-Situationen), *Scale: 1 - 5*

Dark Triad (Naughty Nine - **one narcissism item is missing, sorry...**), *Scale: 1 - 9*

Self-Efficacy (Generalisierte Selbstwirksamkeitserwartung), *Scale: 1 - 6*

Prosocial Tendencies / Altruism (Prosocial Tendencies Measure - Revised), *Scale: 1 - 5*

Trait Anxiety (State-Trait-Anxiety-Inventory), *Scale: 1 - 4*

Trait Anger (State-Trait-Anger-Inventory), *Scale: 1 - 4*

## Internal consistencies, Means and Standard Deviations for all Variables

```{r}
library(psych)
library(purrr)
library(dplyr)
library(knitr)
library(kableExtra)

scales_list <- list(
  "Depression"   = c("HU_ADS_01", "HU_ADS_02", "HU_ADS_03", "HU_ADS_04", "HU_ADS_05",
    "HU_ADS_06", "HU_ADS_07", "HU_ADS_08", "HU_ADS_09", "HU_ADS_10",
    "HU_ADS_11", "HU_ADS_12", "HU_ADS_13", "HU_ADS_14", "HU_ADS_15",
    "HU_ADS_16", "HU_ADS_17", "HU_ADS_18", "HU_ADS_19", "HU_ADS_20"),
  "Trust: Willingness to Interact" = c("AT01_01", "AT01_02", "AT01_03"),
  "Trust: Feeling Secure with the Automation" = c("AT01_04", "AT01_05", "AT01_06"),
  "Trust: Propensity to Trust Humans" = c("AT01_07", "AT01_08", "AT01_09", "AT01_10", "AT01_11"),
  "Trust: Propensity to Trust Automation" = c("AT01_12", "AT01_13", "AT01_14", "AT01_15"),
  "Trust: Avatar Literacy" = c("AT01_16", "AT01_17", "AT01_18"),
  "Trust in Automation (Summary)" = c("AT01_01", "AT01_02", "AT01_03", "AT01_04", "AT01_05", "AT01_06", "AT01_12", "AT01_13", "AT01_14", "AT01_15", "AT01_16", "AT01_17", "AT01_18"),
  "Extraversion" = c("BF01_01", "BF01_06", "BF01_11", "BF01_16"),
  "Agreeableness" = c("BF01_02", "BF01_07", "BF01_12", "BF01_17"),
  "Conscientiousness" = c("BF01_03", "BF01_08", "BF01_13", "BF01_18"),
  "Neuroticism" = c("BF01_04", "BF01_09", "BF01_14", "BF01_19"),
  "Openess" = c("BF01_05", "BF01_10", "BF01_15", "BF01_20", "BF01_21"),
  "CISS: Task-oriented" = c("CS01_05", "CS01_09", "CS01_12", "CS01_14", "CS01_15", "CS01_19", "CS01_23", "CS01_24"),
  "CISS: Emotion-oriented" = c("CS01_02", "CS01_03", "CS01_07", "CS01_08", "CS01_11", "CS01_13", "CS01_16", "CS01_21"),
  "CISS: Avoidance-oriented" = c("CS01_01", "CS01_17", "CS01_18", "CS01_20", "CS01_04", "CS01_06", "CS01_10", "CS01_22"),
  "Machiavellianism" = c("DT01_01", "DT01_04", "DT01_07"),
  "Psychopathy" = c("DT01_02", "DT01_05", "DT01_08"),
  "Narcissism" = c("DT01_03", "DT01_06"),
  "Self-Efficacy" = c("GS01_07", "GS01_09", "GS01_18", "GS01_24", "GS01_25", "GS01_27", "GS01_30", "GS01_31", "GS01_35", "GS01_38"),
  "Altruism" = c("PT01_04", "PT01_10", "PT01_16", "PT01_20", "PT01_23", "PT01_24"),
  "Anxiety" = c("SA01_01", "SA01_02", "SA01_03", "SA01_04", "SA01_05", "SA01_06", "SA01_07", "SA01_08", "SA01_09", "SA01_10","SA01_11", "SA01_12", "SA01_13", "SA01_14", "SA01_15", "SA01_16", "SA01_17", "SA01_18", "SA01_19", "SA01_20"),
  "Anger" = c("SX02_01", "SX02_02", "SX02_03", "SX02_04", "SX02_05",
         "SX02_06", "SX02_07", "SX02_08", "SX02_09", "SX02_10")
)

alpha_summary <- map_dfr(scales_list, function(items) {
  res <- psych::alpha(data_basic[, items], warnings = FALSE)
  return(res$total)
}, .id = "Scale")

# Format and style with kableExtra
alpha_summary %>%
  select(Scale, raw_alpha, std.alpha, average_r, mean, sd) %>%
  kable(
    digits = 2, 
    caption = "Summary of Scale Reliabilities",
    col.names = c("Scale", "Raw Alpha", "Std. Alpha", "Avg r", "Mean", "SD"), # Nice column names!
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    full_width = TRUE, 
    position = "center"
  ) %>%
  row_spec(0:nrow(alpha_summary), extra_css = "padding: 12px 8px;") # 2. Add custom padding to spread rows out

```

### Distribution of variables

<details>

<summary><b>Click to expand.</b></summary>

```{r}
hist(data_basic$depression)
hist(data_basic$trust_wia)
hist(data_basic$trust_secure)
hist(data_basic$trust_humans)
hist(data_basic$trust_automation)
hist(data_basic$trust_literacy)
hist(data_basic$trust_automation_all)
hist(data_basic$extraversion)
hist(data_basic$agreeablenesss)
hist(data_basic$conscientiousness)
hist(data_basic$neuroticism)
hist(data_basic$openess)
hist(data_basic$ciss_task)
hist(data_basic$ciss_emotion)
hist(data_basic$ciss_avoidance)
hist(data_basic$machiavellianism)
hist(data_basic$psychopathy)
hist(data_basic$narcissism)
hist(data_basic$self_efficacy)
hist(data_basic$proso_tend)
hist(data_basic$anxiety)
hist(data_basic$anger)
```


## Intercorrelations of all variables

```{r}
library(tidyverse)
library(Hmisc)
library(knitr)
library(kableExtra)

# 1. Select your target variables
vars <- data_basic %>% 
  select(depression, psychopathy, machiavellianism, narcissism, trust_humans, trust_automation_all, extraversion, agreeablenesss, conscientiousness, openess, ciss_task, ciss_emotion, ciss_avoidance, self_efficacy, proso_tend, anxiety, anger)

# 2. Compute Correlations AND p-values
cor_results <- rcorr(as.matrix(vars))
r_mat       <- cor_results$r
p_mat       <- cor_results$P

# 3. Format values: Apply cell_spec(..., bold = TRUE) for significant cells
cor_formatted <- matrix("", nrow = nrow(r_mat), ncol = ncol(r_mat))

for (i in 1:nrow(r_mat)) {
  for (j in 1:ncol(r_mat)) {
    val <- sprintf("%.2f", r_mat[i, j]) %>% 
      gsub("^0\\.", ".", .) %>% 
      gsub("^-0\\.", "-.", .)
    
    if (!is.na(p_mat[i, j]) && p_mat[i, j] < .05) {
      # Use cell_spec to force true HTML bold formatting
      cor_formatted[i, j] <- cell_spec(val, "html", bold = TRUE)
    } else {
      # Keep non-significant values plain
      cor_formatted[i, j] <- val
    }
  }
}

# 4. Blank out upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 5. Build final data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  cor_formatted,
  check.names = FALSE
)

colnames(final_table)[2:ncol(final_table)] <- 1:ncol(vars)

# 6. Render with kableExtra (CRITICAL: escape = FALSE allows HTML formatting)
final_table %>%
  kbl(
    caption   = "Intercorrelation Matrix",
    align     = c("l", rep("c", ncol(vars))),
    row.names = FALSE,
    escape    = FALSE  # <-- Tells kable NOT to convert HTML tags into plain text
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE
  ) %>%
  add_header_above(c(" " = 1, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Bold values indicate statistically significant correlations (p < .05).",
    general_title = "Note: "
  )
```

```{r}
#| fig.width: 15
#| fig.height: 25
#| out.width: "100%"


library(tidyverse)
library(ggcorrplot)

# 1. Select target variables
vars <- data_basic %>% 
  select(depression, psychopathy, machiavellianism, narcissism, trust_humans, trust_automation_all, extraversion, agreeablenesss, conscientiousness, openess, ciss_task, ciss_emotion, ciss_avoidance, self_efficacy, proso_tend, anxiety, anger)

# 2. Compute correlation matrix and p-values
cor_mat <- cor(vars, use = "pairwise.complete.obs")
p_mat   <- cor_pmat(vars)

ggcorrplot(
  cor_mat,
  type        = "lower",        # Display lower triangle only
  hc.order    = FALSE,          # Keep original variable order
  lab         = TRUE,           # Display correlation values on tiles
  lab_size    = 3.5,            # Size of correlation numbers
  colors      = c("#6D9EC1", "white", "#E46726"), # Cool-to-warm palette
  outline.col = "white"
) +
  theme_minimal() +
  # Force x-axis text rotation AFTER applying theme_minimal()
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
  ) +
  labs(title = "Intercorrelation Heatmap")
```
