---
title: "Scenarios EFRE-Study"
author: "Jule Schilling"
date: "2026-07-23"
format: 
  html:
    toc: true
    toc-depth: 4
    toc-expand: true
    toc-title: "Table of Contents"
execute:
  echo: false      # Hides R code globally across all chunks
  warning: false   # Mutes warnings globally
  message: false   # Mutes package loading messages globally
---

```{r setup, include=FALSE}
setwd("~/Desktop/Uni Würzburg/Forschung/EFRE_Studie/Data/Data_EFRE")
load("EFRE_data.Rdata")

library(dplyr)
library(psych)
library(tidyverse)
library(knitr)
library(kableExtra)
library(effectsize)
library(car)

```

In this document: Hypotheses testing.

## Main Scenarios

## Hypothesis 1

<details>
<summary><b>Click to expand.</b></summary>

H1: Higher trait values in depression are related to withdrawal behavior in automated work situations.

**--> H1 was supported across all scenarios.**

**Depression**

SC06,SC12,SC13,SC14,SC15

\_01 ... ziehe ich mich zurück und warte wie sich die Situation entwickelt.

\_02 ... denke ich, dass die Aufgabenerfüllung sowieso nichts bringt.

\_08 ... bin ich mir sicher, dass ich die Aufgabe erfüllen kann. (R)

\_04 ... habe ich die Energie, um die Aufgabe anzugehen. (R)

#### Scenario 1

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC06_01, SC06_02, SC06_08, SC06_04, depression, psychopathy, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 1: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 2

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC12_01, SC12_02, SC12_08, SC12_04, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 2: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 3

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC13_01, SC13_02, SC13_08, SC13_04, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 3: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 4

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC14_01, SC14_02, SC14_08, SC14_04, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 4: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 5

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC15_01, SC15_02, SC15_08, SC15_04, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 5: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

## Hypothesis 2

<details>
<summary><b>Click to expand.</b></summary>

H2: Higher trait values in psychopathy are related to selfish and less empathic behavior in automated work situations.

**--> H2 was partly supported.**

**Psychopathy**

SC07,SC16,SC17,SC18,SC19

\_09 ... täusche ich vor, für die Aufgabe zu beschäftigt zu sein.

\_10 ... versuche ich möglichst viele Vorteile für andere Mitarbeitende herauszuholen. (R)

\_11 ... sind mir die Befindlichkeiten anderer Mitarbeitenden wichtig.(R)

\_12 ... kann ich auch mal harte Entscheidungen treffen, die andere Mitarbeitende nicht fällen würden.

#### Scenario 1

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC07_09, SC07_10, SC07_11, SC07_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 1: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 2

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC16_09, SC16_10, SC16_11, SC16_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 2: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 3

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC17_09, SC17_10, SC17_11, SC17_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 3: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 4

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC18_09, SC18_10, SC18_11, SC18_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = TRUE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 4: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 5

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC19_09, SC19_10, SC19_11, SC19_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = TRUE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 5: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```



## Hypothesis 3

<details>
<summary><b>Click to expand.</b></summary>

H3: Higher trait values in trust in automation are related to more trusting behavior in automated work situations.

**--> H3 was supported across all scenarios.**

**Trust**

SC08,SC20,SC21,SC22,SC23

\_13 ... betrachte ich die Automatisierung als eine Art hilfreichen Partner.

\_14 ... ist die Rolle der Automatisierung mit Skepsis zu betrachten. (R)

\_15 ... habe ich Angst vor der Automatisierung. (R)

\_16 ... vertraue ich auf die Automatisierung.

#### Scenario 1

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC08_13, SC08_14, SC08_15, SC08_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 1: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 2

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC20_13, SC20_14, SC20_15, SC20_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 2: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 3

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC21_13, SC21_14, SC21_15, SC21_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 3: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 4

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC22_13, SC22_14, SC22_15, SC22_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = TRUE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 4: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 5

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC23_13, SC23_14, SC23_15, SC23_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = TRUE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 5: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

## Leadership scenarios

## Leader's perspective: coercive behavior

## Hypothesis 4

<details>
<summary><b>Click to expand.</b></summary>

H4: Higher trait values in psychopathy are associated with more coercive behavior.

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SL04_08, SL04_04, SL04_10, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario Leadership: Coersive Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

## Leader's perspective: cooperative behavior

## Hypothesis 5,6,7,8

<details>
<summary><b>Click to expand.</b></summary>


H5: Higher trait values in trust are associated with more cooperative behavior.

H6: Higher trait values in prosocial tendencies are associated with more cooperative behavior.

H7: Higher trait values in agreeableness are associated with more cooperative behavior.

H8: Higher trait values in self-efficacy are associated with more cooperative behavior.

--> partly supported; mostly unexpected effects for item 3 "...stelle ich eine Bonuszahlung in Aussicht, wenn die Zielvorgaben erfüllt werden. "


```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SL04_01, SL04_02, SL04_09, trust_automation_all, trust_humans, proso_tend, agreeablenesss, self_efficacy, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario Leadership: Cooperative Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

## Order effect

## Hypothesis 9

<details>
<summary><b>Click to expand.</b></summary>

H9: Cooperative behavior is higher when participants are first presented with the employees’ perspective (i.e., employees’ perspective first) than if they are first presented with the leaders’ perspective (i.e., leaders’ perspective first)

Employee first - Leader first; positive values indicate that there is more cooperative behavior when the employee scenario is presented first

Expected "empathy effect" for item: "Suche ich das Gespräch mit den Mitarbeitenden, wann die geleisteten Überstunden wieder abgebaut werden können."; no effect for other items --> Hypothesis partly supported

```{r}
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))

# Compare means for cooperation: leadership scenario
means_order_effect_leadership_cooperation <- data_basic %>%
  group_by(order_leadership) %>%
  summarise(
    across(
      .cols = c(SL04_01, SL04_02, SL04_09), 
      .fns = ~ mean(.x, na.rm = TRUE),            
      .names = "mean_{.col}"                      
    ),
    .groups = 'drop'
  )
t.test(SL04_01 ~ order_leadership, data = data_basic)
cohens_d(SL04_01 ~ order_leadership, data = data_basic)

t.test(SL04_02 ~ order_leadership, data = data_basic)
cohens_d(SL04_02 ~ order_leadership, data = data_basic)

t.test(SL04_09 ~ order_leadership, data = data_basic)
cohens_d(SL04_09 ~ order_leadership, data = data_basic)
```

## Hypothesis 10

<details>
<summary><b>Click to expand.</b></summary>

H10: Coersive behavior is lower when participants are first presented with the employees’ perspective than if they are first presented with the leaders’ perspective

Employee first - Leader first; positive values indicate that there is more coersive behavior when the employee scenario is presented first

Expected "empathy effect" for all items. Hypothesis was supported for all items.


```{r}
means_order_effect_leadership_coersive <- data_basic %>%
  group_by(order_leadership) %>%
  summarise(
    across(
      .cols = c(SL04_08, SL04_04, SL04_10), 
      .fns = ~ mean(.x, na.rm = TRUE),            
      .names = "mean_{.col}"                      
    ),
    .groups = 'drop'
  )

t.test(SL04_08 ~ order_leadership, data = data_basic)
cohens_d(SL04_08 ~ order_leadership, data = data_basic)

t.test(SL04_04 ~ order_leadership, data = data_basic)
cohens_d(SL04_04 ~ order_leadership, data = data_basic)

t.test(SL04_10 ~ order_leadership, data = data_basic)
cohens_d(SL04_10 ~ order_leadership, data = data_basic)
```


## Employee's perspective: reactant behavior

## Hypothesis 11, 14, 16

<details>
<summary><b>Click to expand.</b></summary>

H11: Lower trait values in agreeableness are associated with more reactant behavior.

H14: Higher trait values in psychopathy are associated with more reactant behavior.

H16: Higher trait values in depression are associated with more reactant behavior.

--> agreeableness not supported; depression and psychopathy partly supported.

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SL05_01, SL05_05, SL05_06, agreeablenesss, psychopathy, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario Employsee: Reactant Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

## Employee's perspective: cooperative behavior

## Hypothesis 12, 13, 15

<details>
<summary><b>Click to expand.</b></summary>

H12: Higher trait values in conscientiousness are associated with more cooperative behavior.

H13: Higher trait values in agreeableness are associated with more cooperative behavior.

H15: Higher trait values in trust are associated with more cooperative behavior.


---> all hypotheses partly supported


```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SL05_02, SL05_03, SL05_04, conscientiousness, agreeablenesss, trust_humans, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario Employsee: Reactant Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```


## Order effect

## Hypothesis 17

<details>
<summary><b>Click to expand.</b></summary>

H17: Cooperative behavior is higher when participants are first presented with the leaders’ perspective than if they are first presented with the employees’ perspective.

Employee first - Leader first; positive values indicate that there is more cooperative behavior when the employee scenario is presented first

Expected "empathy effect" for none of the items. However d =.2 for item "suche ich das Gespräch mit der Führungskraft, um über die hohe Arbeitsbelastung zu sprechen."

--> Hypothesis not supported

```{r}
# Compare means for cooperation: employee scenario
means_order_effect_employee_cooperation <- data_basic %>%
  group_by(order_leadership) %>%
  summarise(
    across(
      .cols = c(SL05_02, SL05_03, SL05_04), 
      .fns = ~ mean(.x, na.rm = TRUE),            
      .names = "mean_{.col}"                      
    ),
    .groups = 'drop'
  )

t.test(SL05_02 ~ order_leadership, data = data_basic)
cohens_d(SL05_02 ~ order_leadership, data = data_basic)

t.test(SL05_03 ~ order_leadership, data = data_basic)
cohens_d(SL05_03 ~ order_leadership, data = data_basic)

t.test(SL05_04 ~ order_leadership, data = data_basic)
cohens_d(SL05_04 ~ order_leadership, data = data_basic)


```


## Hypothesis 18

<details>
<summary><b>Click to expand.</b></summary>

H18: Reactant behavior is lower when participants are first presented with the leaders’ perspective than if they are first presented with the employees’ perspective.

Employee first - Leader first; positive values indicate that there is more reactant behavior when the employee scenario is presented first

More reactant behavior when first presented with leadership scenario for item: "äußere ich meinen Unmut über die Situation beim Betriebsrat"

--> hypothesis not supported

```{r}
means_order_effect_employee_reactant <- data_basic %>%
  group_by(order_leadership) %>%
  summarise(
    across(
      .cols = c(SL05_01, SL05_05, SL05_06), 
      .fns = ~ mean(.x, na.rm = TRUE),            
      .names = "mean_{.col}"                      
    ),
    .groups = 'drop'
  )

t.test(SL05_01 ~ order_leadership, data = data_basic)
cohens_d(SL05_01 ~ order_leadership, data = data_basic)

t.test(SL05_05 ~ order_leadership, data = data_basic)
cohens_d(SL05_05 ~ order_leadership, data = data_basic)

t.test(SL05_06 ~ order_leadership, data = data_basic)
cohens_d(SL05_06 ~ order_leadership, data = data_basic)
```

## Interaction order effect with trait variables

## Leadership perspective


## Hypothesis 19

<details>
<summary><b>Click to expand.</b></summary>

H19: If psychopathy is low, the order effect of employees’ perspective first versus leaders’ perspective first on coersive behavior (H10) is higher than if psychopathy is high.

--> not supported

```{r}
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))

data_basic <- data_basic %>% # centering psychopathy
  mutate(
    psychopathy_cent = scale(psychopathy, center = TRUE, scale = FALSE)
  )



# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL04_08 ~ order_leadership * psychopathy_cent, data = data_basic)
Anova(model, type = 3)



```
## Hypotheses 20,21,22

<details>
<summary><b>Click to expand.</b></summary>


H20: If trust is low, the order effect of employees’ perspective first versus leaders’ perspective first on cooperative behavior (H9) is higher than if trust is high.

H21: If prosocial tendencies are low, the order effect of employees’ perspective first versus leaders’ perspective first on cooperative behavior (H9) is higher than if prosocial tendencies are high.

H22: If agreeableness is low, the order effect of employees’ perspective first versus leaders’ perspective first on cooperative behavior (H9) is higher than if agreeableness is high.

--> all hypotheses not supported

```{r}

## leader perspective; coop behav (SL04_01, SL04_02, SL04_09)
# trust
#H20
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))


data_basic <- data_basic %>% # centering trust_all
  mutate(
    trust_all_cent = scale(trust_all, center = TRUE, scale = FALSE)
  )



# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL04_01 ~ order_leadership * trust_all_cent, data = data_basic)
Anova(model, type = 3)



```

```{r}
#H21
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))

# prosocial tendencies
data_basic <- data_basic %>% # centering proso_tend
  mutate(
    proso_tend_cent = scale(proso_tend, center = TRUE, scale = FALSE)
  )
# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL04_01 ~ order_leadership * proso_tend_cent, data = data_basic)
Anova(model, type = 3)
```

```{r}
#H22
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))

# agreeableness
data_basic <- data_basic %>% # centering agreeablenesss
  mutate(
    agreeablenesss_cent = scale(agreeablenesss, center = TRUE, scale = FALSE)
  )
# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL04_01 ~ order_leadership * agreeablenesss_cent, data = data_basic)
Anova(model, type = 3)

```


## Employee's perspective
## Hypothesis 23
<details>
<summary><b>Click to expand.</b></summary>

H23: If psychopathy is low, the order effect of employees’ perspective first versus leaders’ perspective first on reactant behavior (18) is higher than if psychopathy is high.

```{r}

#H23
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))

## employees perspective; reactant behav (SL05_01, SL05_05, SL05_06)
# psychopathy
data_basic <- data_basic %>% # centering psychopathy
  mutate(
    psychopathy_cent = scale(psychopathy, center = TRUE, scale = FALSE)
  )
# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL05_01 ~ order_leadership * psychopathy_cent, data = data_basic)
Anova(model, type = 3)
```

## Hypotheses 24,25,26

<details>
<summary><b>Click to expand.</b></summary>

H24: If trust is low, the order effect of employees’ perspective first versus leaders’ perspective first on cooperative behavior (H17) is higher than if trust is high.

--> supported(?)

H25: If prosocial tendencies are low, the order effect of employees’ perspective first versus leaders’ perspective first on cooperative behavior (H17) is higher than if prosocial tendencies are high.

H26: If agreeableness is low, the order effect of employees’ perspective first versus leaders’ perspective first on cooperative behavior (H17) is higher than if agreeableness is high.

--> H25 & 26 not supported

```{r}
#H24
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))

## employees perspective; coop behav (SL05_02, SL05_03, SL05_04)
# trust
data_basic <- data_basic %>% # centering trust_all
  mutate(
    trust_all_cent = scale(trust_all, center = TRUE, scale = FALSE)
  )
# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL05_02 ~ order_leadership * trust_all_cent, data = data_basic)
Anova(model, type = 3)

```

```{r}
library(sjPlot)
#H24
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))

## employees perspective; coop behav (SL05_02, SL05_03, SL05_04)
# trust
data_basic <- data_basic %>% # centering trust_all
  mutate(
    trust_all_cent = scale(trust_all, center = TRUE, scale = FALSE)
  )

data_basic$trust_all_cent <- as.numeric(data_basic$trust_all_cent)

# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL05_02 ~ order_leadership * trust_all_cent, data = data_basic)
Anova(model, type = 3)



plot_model(model, type = "int")
```

```{r}

#H25
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))


# prosocial tendencies
data_basic <- data_basic %>% # centering proso_tend
  mutate(
    proso_tend_cent = scale(proso_tend, center = TRUE, scale = FALSE)
  )
# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL05_02 ~ order_leadership * proso_tend_cent, data = data_basic)
Anova(model, type = 3)
```

```{r}
#H26
data_basic <- data_basic %>%
  mutate(
    order_leadership = factor(
      case_when(
      ZU02_01 == 1 ~ "leader first",
      ZU02_02 == 1 ~ "employee first",
      TRUE         ~ NA_character_  # Handles cases where neither is 1 (optional)
    )
  ))

# agreeableness
data_basic <- data_basic %>% # centering agreeablenesss
  mutate(
    agreeablenesss_cent = scale(agreeablenesss, center = TRUE, scale = FALSE)
  )
# Anova
options(contrasts = c("contr.sum", "contr.poly"))
model <- lm(SL05_02 ~ order_leadership * agreeablenesss_cent, data = data_basic)
Anova(model, type = 3)

```


