---
title: "Scenarios EFRE-Study"
author: "Jule Schilling"
date: "2026-07-23"
format: 
  html:
    toc: true
    toc-depth: 4
    toc-expand: true
    toc-title: "Table of Contents"
execute:
  echo: false      # Hides R code globally across all chunks
  warning: false   # Mutes warnings globally
  message: false   # Mutes package loading messages globally
---

```{r setup, include=FALSE}
setwd("~/Desktop/Uni Würzburg/Forschung/EFRE_Studie/Data/Data_EFRE")
load("EFRE_data.Rdata")

library(dplyr)
library(psych)
library(tidyverse)
library(knitr)
library(kableExtra)

```

In this document: Hypotheses testing.

## Main Scenarios

## Hypothesis 1

<details>
<summary><b>Click to expand.</b></summary>

H1: Higher trait values in depression are related to withdrawal behavior in automated work situations.

**--> H1 was supported across all scenarios.**

**Depression**

SC06,SC12,SC13,SC14,SC15

\_01 ... ziehe ich mich zurück und warte wie sich die Situation entwickelt.

\_02 ... denke ich, dass die Aufgabenerfüllung sowieso nichts bringt.

\_08 ... bin ich mir sicher, dass ich die Aufgabe erfüllen kann. (R)

\_04 ... habe ich die Energie, um die Aufgabe anzugehen. (R)

#### Scenario 1

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC06_01, SC06_02, SC06_08, SC06_04, depression, psychopathy, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 1: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 2

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC12_01, SC12_02, SC12_08, SC12_04, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 2: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 3

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC13_01, SC13_02, SC13_08, SC13_04, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 3: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 4

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC14_01, SC14_02, SC14_08, SC14_04, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 4: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 5

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC15_01, SC15_02, SC15_08, SC15_04, depression)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 5: Depression Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

## Hypothesis 2

<details>
<summary><b>Click to expand.</b></summary>

H2: Higher trait values in psychopathy are related to selfish and less empathic behavior in automated work situations.

**--> H2 was partly supported.**

**Psychopathy**

SC07,SC16,SC17,SC18,SC19

\_09 ... täusche ich vor, für die Aufgabe zu beschäftigt zu sein.

\_10 ... versuche ich möglichst viele Vorteile für andere Mitarbeitende herauszuholen. (R)

\_11 ... sind mir die Befindlichkeiten anderer Mitarbeitenden wichtig.(R)

\_12 ... kann ich auch mal harte Entscheidungen treffen, die andere Mitarbeitende nicht fällen würden.

#### Scenario 1

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC07_09, SC07_10, SC07_11, SC07_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 1: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 2

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC16_09, SC16_10, SC16_11, SC16_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 2: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 3

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC17_09, SC17_10, SC17_11, SC17_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 3: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 4

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC18_09, SC18_10, SC18_11, SC18_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = TRUE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 4: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 5

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC19_09, SC19_10, SC19_11, SC19_12, psychopathy, depression, trust_automation_all)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = TRUE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 5: Psychopathy Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```



## Hypothesis 3

<details>
<summary><b>Click to expand.</b></summary>

H3: Higher trait values in trust in automation are related to more trusting behavior in automated work situations.

**--> H3 was supported across all scenarios.**

**Trust**

SC08,SC20,SC21,SC22,SC23

\_13 ... betrachte ich die Automatisierung als eine Art hilfreichen Partner.

\_14 ... ist die Rolle der Automatisierung mit Skepsis zu betrachten. (R)

\_15 ... habe ich Angst vor der Automatisierung. (R)

\_16 ... vertraue ich auf die Automatisierung.

#### Scenario 1

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC08_13, SC08_14, SC08_15, SC08_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 1: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 2

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC20_13, SC20_14, SC20_15, SC20_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 2: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 3

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC21_13, SC21_14, SC21_15, SC21_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 3: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 4

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC22_13, SC22_14, SC22_15, SC22_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = TRUE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 4: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

#### Scenario 5

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SC23_13, SC23_14, SC23_15, SC23_16, trust_automation_all, trust_humans, depression, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = TRUE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario 5: Trust Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = FALSE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

## Leadership scenarios

## Leader's perspective: coercive behavior

## Hypothesis 4

<details>
<summary><b>Click to expand.</b></summary>

H4: Higher trait values in psychopathy are associated with more coercive behavior.

```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SL04_08, SL04_04, SL04_10, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario Leadership: Coersive Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```

## Leader's perspective: cooperative behavior

## Hypothesis 5,6,7,8

<details>
<summary><b>Click to expand.</b></summary>


H5: Higher trait values in trust are associated with more cooperative behavior.

H6: Higher trait values in prosocial tendencies are associated with more cooperative behavior.

H7: Higher trait values in agreeableness are associated with more cooperative behavior.

H8: Higher trait values in self-efficacy are associated with more cooperative behavior.

--> partly supported; mostly unexpected effects for item 3 "...stelle ich eine Bonuszahlung in Aussicht, wenn die Zielvorgaben erfüllt werden. "


```{r}
# 1. Select your target subset
vars <- data_basic %>% 
  select(SL04_01, SL04_02, SL04_09, trust_automation_all, trust_humans, proso_tend, agreeablenesss, self_efficacy, psychopathy)

# 2. Calculate Means and SDs across all columns automatically
means <- colMeans(vars, na.rm = TRUE)
sds   <- apply(vars, 2, sd, na.rm = TRUE)

# 3. Calculate Correlation Matrix (your code)
cor_mat <- cor(vars, use = "pairwise.complete.obs") %>% round(2)

# Format correlations (remove leading 0s for APA style)
cor_formatted <- apply(cor_mat, c(1, 2), function(x) {
  sprintf("%.2f", x) %>% gsub("^0\\.", ".", .) %>% gsub("^-0\\.", "-.", .)
})

# Blank out the upper triangle and diagonal
cor_formatted[upper.tri(cor_formatted, diag = TRUE)] <- ""

# 4. Combine into a single table data frame
final_table <- data.frame(
  Variable = paste0(1:ncol(vars), ". ", colnames(vars)),
  M        = sprintf("%.2f", means),
  SD       = sprintf("%.2f", sds),
  cor_formatted,
  check.names = FALSE
)

# Rename correlation columns to 1, 2, 3, 4 to save horizontal space
colnames(final_table)[4:ncol(final_table)] <- 1:ncol(vars)

# 5. Display with kableExtra
final_table %>%
  kbl(
    caption   = "Scenario Leadership: Cooperative Items",
    align     = c("l", "c", "c", rep("c", ncol(vars))),
    row.names = FALSE
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width        = TRUE
  ) %>%
  add_header_above(c(" " = 3, "Correlations" = ncol(vars))) %>%
  footnote(
    general       = "Scale: 1 - 100.",
    general_title = "Note: "
  )
```






